\documentclass[12pt, letterpaper]{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}

\title{DAT510 - Assignment 2}
\author{Fr\o ydis J\o rgensen}

\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}

\begin{abstract}
A one-paragraph summary of the entire assignment - your choices of cryptographic primitives and their parameters,
procedure, test results, and analysis. 
\end{abstract}

\section*{Introduction}
A description of the scientific background for your project, including previous work that your project builds on.
(Remember to cite your sources!) The final sentence (analogous to the thesis statement in a term paper) is the
objective of your experiment. 

\section*{Design and Implementation}
A detailed description (in paragraph format) of the design, procedure, and implementation of your project. This
should be the main part of the report. 

\section*{Test results}
Results of testing the software, as you observed/recorded them. Note that this section is only for observations you
make during testing. Your analysis belongs in the Discussion section. 

\section*{Discussion}
Your analysis of what your testing results mean, and your analysis.

\section*{Conclusion}
A short paragraph that restates the objective from your introduction and relates it to your results and discussion, and
describes any future improvements that you would recommend. Works Cited A bibliography of all of the sources
you got information from in your report. 


\begin{thebibliography}{10} 
\bibitem{BBS} A Security site,  \emph{Explaines how Blum Blum Shub works},
\url{https://www.asecuritysite.com/encryption/blum}.
\bibitem{DH} Wikipedia,  \emph{Wikipedia - Diffie-Hellman},
\url{https://en.wikipedia.org/wiki/Diffie%E2%80%93Hellman_key_exchange}.
\end{thebibliography}



\end{document}