\documentclass[12pt, letterpaper]{article}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}

\title{DAT510 - Assignment 2}
\author{Fr\o ydis J\o rgensen}

\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}

\begin{abstract}
A one-paragraph summary of the entire assignment - your choices of cryptographic primitives
and their parameters, procedure, test results, and analysis.
\end{abstract}

\section*{Introduction}
A description of the scientific background for your project, including previous work that your
project builds on. (Remember to cite your sources!) The final sentence (analogous to the thesis
statement in a term paper) is the objective of your experiment.

\section*{Design and Implementation}
A detailed description (in paragraph format) of the design, procedure, and implementation of
your project. This should be the main part of the report.

\section*{Test results}
Results of testing the software, as you observed/recorded them. Note that this section is only for
observations you make during testing. Your analysis belongs in the Discussion section.

\section*{Discussion}
Your analysis of what your testing results mean, and your analysis.

\section*{Conclusion}
A short paragraph that restates the objective from your introduction and relates it to your results
and discussion, and describes any future improvements that you would recommend. Works Cited A
bibliography of all of the sources you got information from in your report.

\newpage
\begin{thebibliography}{10} 
\bibitem{SE} StackExchange,  \emph{Algorithm to find unknown patterns in a string},
\url{https://cs.stackexchange.com/questions/79182/im-looking-for-an-algorithm-to-find-unknown-patterns-in-a-string}.
\bibitem{SO} StackOverflow, \emph{Index of duplicated items},
\url{https://stackoverflow.com/questions/5419204/index-of-duplicates-items-in-a-python-list}
\bibitem{chi} Practical cryptography, \emph{Chi-squared Statistic},
\url{http://practicalcryptography.com/cryptanalysis/text-characterisation/chi-squared-statistic/#javascript-chi-squared-calculator}
\bibitem{vigenere} Practical cryptography, \emph{Cryptoanalysis of the Vigenere Cipher},
\url{http://practicalcryptography.com/cryptanalysis/stochastic-searching/cryptanalysis-vigenere-cipher/}
\end{thebibliography}



\end{document}